\Large \bf New Static Analysis Techniques to Detect Entropy Failure Vulnerabilities in Modern Software Projects

### 2018-12-14 paper/paper.tex

\begin{abstract}
 Test abstract
\end{abstract}

@@

\subsection{Predicate Abstraction}

@@

\begin{itemize}
    \item $b \gets \mathsf{Verify}_{L}(\pi, P)$: Takes as input a $1$-safety property $\pi$ and a program $P$ and outputs an accepting bit $\top$ if
    $P$ satisfies the safety property, and otherwise outputs a rejecting bit $\bot$ or fails to terminate otherwise.
\end{itemize}

@@

\subsection{Naive Product Program Inference Rules}

@@

\subsection{Taint-augmented Inference Rules}

@@

@@

Description of algorithm using the two subroutines above.

@@

Verify the following conjectures. Prove that a heuristic-based approach is no less powerful than a full product program approach.
Run this tool on projects in the wild to determine how widespread entropy-misuse bugs are among software projects ``in the wild.''

>>>>

\begin{abstract}
    In this work we examine the problem of entropy misuse vulnerabilities in
    security-critical software. Our work approaches the problem from an
    ``ounce of prevention is worth a pound of cure'' perspective; by introducing
    and applying a novel static analysis technique \emph{differential taint analysis},
    we propose a method for catching these bugs. Our approach
    leverages modern software development's
     common practice of maintaining software version history to 
     provide augmented heuristics to standard static analysis tools.
\end{abstract}

@@

\subsection{Predicate Abstraction}
\label{sec:predabstraction}

@@

\begin{itemize}
    \item $b \gets \mathsf{Verify}_{L}(\Pi, P)$: Takes as input a set $\Pi$ of $1$-safety properties and a program $P$ and outputs an accepting bit $\top$ if
    $P$ satisfies all $\pi \in \Pi$, and otherwise outputs a rejecting bit $\bot$ or fails to terminate otherwise.
\end{itemize}

@@

\subsection{Basic Product Program Inference Rules}
\label{sec:basicpprules}

@@

\subsection{Taint-augmented Inference Rules}
\label{sec:augpprules}

@@

Formally, we define the following algorithm:

\begin{itemize}
    \item $P_1 \times P_2 \gets \mathsf{Prod}_R(P_1, P_2, \Gamma)$: Given two programs $P_1$ and $P_2$, a taint environment (mapping of program statements) to 
    taint values), and a set of inference rules $R$ we output the product program $P_1 \times P_2$.
\end{itemize}

@@

Let $\Delta$ be some set of entropy-preserving operations in our language $L$ with some set of 
natural taint propagation rules $S$.
Let $R$ be our set of inference rules described in Sections \ref{sec:basicpprules} and \ref{sec:augpprules}.
Using the subroutines we described above and the verification method in Section
\ref{sec:predabstraction}, we have the following algorithm:

\begin{itemize}
    \item $b \gets \mathsf{DifferentialTaintAnalysis}_\Delta(P_1, P_2, \Sigma, Z)$: We take 
    as input two programs $P_1$ and $P_2$, a set of sources $\Sigma$, and a set of 
    sinks $Z$. We then compute:
    \begin{itemize}
        \item $(\Gamma_1, P_1') \gets \mathsf{Instrument}(P_1, \mathsf{Taint}_{S,L}, \Sigma, \Delta)$
        \item $(\Gamma_2, P_2') \gets \mathsf{Instrument}(P_2, \mathsf{Taint}_{S,L}, \Sigma, \Delta)$
        \item $P'_1 \times P'_2 \gets \mathsf{Prod}_R(P'_1, P'_2, \Gamma_1 \cup \Gamma_2)$
    \end{itemize}
    At each synchronized sink pair $(\zeta_1, \zeta_2) \in Z$ in $P'_1 \times P'_2$, add an assertion of equality 
    $(\zeta_1 = \zeta_2)$ to a set of safety properties $\Pi$. Then compute $b \gets \mathsf{Verify}_{L}(\Pi, P'_1 \times P'_2)$
    and output $b$.
\end{itemize}

@@

In continuing this work, we would like to pursue a couple main lines of inquiries:

\begin{itemize}
    \item We wish to see how much our taint-augmented inference rules aid the verifier, from an experimental perspective on large projects such as OpenSSL.
    \item We wish to prove that our taint-augmented inferences rules (or some superset of them) are ``just as useful'' as the basic rules (that is,
    our verifier does not lose any information from using the scoped-down rules).
    \item We want a formal reduction between a notion of differential taint analysis and the approach described here.
    \item Create a push-button software solution for large projects, suitable for insertion in a continuous integration development cycle.
    \item Take an at-large survey of open-source software for entropy misuse vulnerabilities.
\end{itemize}
